Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

\medskip
Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space. Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}. Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}. Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
\begin{eqnarray}
 && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
 &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
 &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
\label{global_mass_balance}
\end{eqnarray}

@@

\medskip
The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}. The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.

>>>>

\medskip
Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space. Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}. 
%Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}. 
Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
\begin{eqnarray}
 && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
 &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
 &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
\label{global_mass_balance}
\end{eqnarray}

@@

%\medskip
%The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}. The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
